Counting And Confusion: Bayesian Rate Estimation With Multiple Populations

### 2012-12-16 many.tex
curt made tiny change in title and added acknowledgements

\title{Counting With Confusion: Bayesian Rate Estimation With Multiple
  Populations}

@@

\begin{acknowledgments}
  We thank Kipp Cannon, Chad Hanna, Drew Keppel, Richard
  O'Shaughnessy, and Ted von Hippel for discussions and suggestions
  about this manuscript.  IM and WMF thank KITP.
\end{acknowledgments}

>>>>

\title{Counting And Confusion: Bayesian Rate Estimation With Multiple
  Populations}

@@

\begin{acknowledgments}
  We thank Kipp Cannon, Chad Hanna, Drew Keppel, Richard
  O'Shaughnessy, and Ted von Hippel for discussions and suggestions
  about this manuscript.  IM and WMF thank KITP.  CC's work was carried out  at the Jet Propulsion Laboratory, California Institute of Technology, under contract to the National Aeronautics and Space Administration.  CC also gratefully acknowledges support from NSF grant PHY1068881.  Copyright 2012.  All rights reserved.
\end{acknowledgments}
